DNSKEY Management

### 2012-12-05 paper/paper.tex
break

\subsection{Disabling DNSSEC}

\section{Case-Study: \texttt{ch.} Zone\wbts}
\label{sec:case-study}

>>>>

\subsection{Disabling DNSSEC}
The final and somewhat unintuitive managerial issue with DNSSEC is what needs to be done once a registrant wishes to turn it off.

In such a case, it is absolutely insufficient to only turn off the service on the devices serving the aforementioned  zone: in doing so, resolvers won't be able to distinguish between spoofed DNS replies that contain non-DNSSEC data and legitimate replies that simply stopped using DNSSEC.

For
\section{Case-Study: \texttt{ch.} Zone\wbts}
\label{sec:case-study}
